User-level Grid Monitoring with Inca 2

### 2007-04-17 papers/hpdc-gmw-2007/gmw01c-smallen.tex
rename to include last name not email address
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6861 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3
more name changes
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6862 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3
embed bbl into tex as asked by sheridan
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6863 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

%------------------------------------------------------------------------- 
\bibliographystyle{abbrv}
\bibliography{paper}

>>>>

\bibliographystyle{abbrv}
\begin{thebibliography}{10}

\bibitem{gridice}
S.~Andreozzi, N.~D. Bortoli, S.~Fantinel, A.~Ghiselli, G.~L. Rubini,
  G.~Tortone, and M.~C. Vistoli.
\newblock {GridICE: a monitoring service for Grid systems}.
\newblock {\em {Future Generation Computer Systems}}, 21(4):559--571, 2005.

\bibitem{grasp}
G.~Chun, H.~Dail, H.~Casanova, and A.~Snavely.
\newblock {Benchmark Probes for Grid Assessment}.
\newblock April 2004.

\bibitem{clumon}
{Clumon Web page}.
\newblock \url{http://clumon.ncsa.uiuc.edu}, 2007.

\bibitem{apt}
{Debian -- The Universal Operating System}.
\newblock \url{http://www.debian.org}, 2007.

\bibitem{deisa}
{Deisa - Distributed European Infrastructure for Supercomputing Appications}.
\newblock \url{http://www.deisa.eu/}, 2007.

\bibitem{globus}
I.~Foster and C.~Kesselman.
\newblock {Globus: A Metacomputing Infrastructure Toolkit}.
\newblock {\em International Journal of Supercomputer Applications},
  11(2):115--128, 1997.

\bibitem{hibernate}
{Hibernate Web page}.
\newblock \url{http://www.hibernate.org}, 2007.

\bibitem{jetty}
{Jetty Web page}.
\newblock \url{http://jetty.mortbay.org}, 2007.

\bibitem{grasp2}
O.~Khalili, J.~He, C.~Olschanowsky, A.~Snavely, and H.~Casanova.
\newblock {Measuring the Performance and Reliability of Production
  Computational Grids}.
\newblock September 2006.

\bibitem{monalisa}
I.~Legrand, H.~Newman, R.~Voicu, C.~Cirstoiu, C.~Grigoras, M.~Toarta, and
  C.~Dobre.
\newblock {MonALISA: An Agent based, Dynamic Service System to Monitor, Control
  and Optimize Grid based Applications}.
\newblock In {\em CHEP 2004}, Interlaken, Switzerland, September 2004.

\bibitem{log4j}
{Log4J Project Web page}.
\newblock \url{http://logging.apache.org/log4j}, 2007.

\bibitem{ganglia}
M.~Massie, B.~Chun, and D.~Culler.
\newblock { The Ganglia Distributed Monitoring System: Design, Implementation,
  and Experience}.
\newblock {\em Parallel Computing}, April 2004.

\bibitem{mom}
{Microsoft Operations Manager}.
\newblock \url{http://www.microsoft.com/mom}, 2007.

\bibitem{myproxy}
{MyProxy Credential Management Service}.
\newblock \url{http://myproxy.ncsa.uiuc.edu}, 2007.

\bibitem{ngs}
{NGS Web page}.
\newblock \url{http://www.grid-support.ac.uk}, 2007.

\bibitem{ncsa-test}
{NCSA TestGrid Project}.
\newblock \url{http://grid.ncsa.uiuc.edu/test}, 2007.

\bibitem{nagios}
{Nagios Web page}.
\newblock \url{http://www.nagios.org}, 2007.

\bibitem{geon}
A.~K. Sinha, B.~Ludaescher, B.~Brodaric, C.~Baru, D.~Seber, A.~Snoke, and
  C.~Barnes.
\newblock { GEON: Developing the Cyberinfrastructure for the Earth Sciences - A
  Workshop Report on Intrusive Igneous Rocks, Wilson Cycle and Concept Spaces}.
\newblock {\em Submitted to GSA Today}.

\bibitem{inca1}
S.~Smallen, C.~Olschanowsky, K.~Ericson, P.~Beckman, and J.~M. Schopf.
\newblock {The Inca Test Harness and Reporting Framework}.
\newblock In {\em Proceedings of Supercomputing 04}, November 2004.

\bibitem{teragrid}
{The TeraGrid Project Web page}.
\newblock \url{http://www.teragrid.org}, 2007.

\bibitem{tivoli}
{IBM Tivoli Monitoring Web page}.
\newblock \url{http://www.ibm.com/software/tivoli/products/monitor/}, 2007.

\bibitem{gits}
{The UK Grid Integration Test Script - GITS}.
\newblock \url{http://www.soton.ac.uk/~djb1/gits.html}, 2007.

\bibitem{webalizer}
{Webalizer Web page}.
\newblock \url{http://www.mrunix.net/webalizer/}, 2007.

\end{thebibliography}
